\documentclass[11pt,fleqn]{article}
\usepackage{url}
\setlength {\topmargin} {-.15in}
\setlength {\textheight} {8.6in}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{color}
\usepackage[normalem]{ulem}

\title{SE 3XA3: Problem Statement\\DJ.Js}
\author{Group 12, Dynamic Play\\
Amandeep Panesar - panesas2 \\ Victor Velechovsky - velechva \\ Taha Mian - maintm}
\date{\today}


\begin{document}
\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
September 22nd 2016 & Taha Mian & Intialize the tex file\\
September 22nd 2016 & Victor Velechovsky & First Draft\\
September 22nd 2016 & Amandeep Panesar & First Draft\\
December  6th  2016 & Victor Velechovsky & Revision 1\\
\bottomrule
\end{tabularx}
\end{table}
\maketitle
%\newpage

\section{The Problem}

\textcolor{blue}{
Social gatherings where nobody likes the music can be a drag. Poor choice of music can make events boring and unenjoyable.
}

\section{How We Will Solve It}
\textcolor{blue} {
We will bad music at social gatherings by creating a democratic voting system which allows all opinions to be heard. The voting system will give users the ability to change the music to their liking.
}

\section{Why is this an important Problem?}
The problem is important to end users because it gives party hosts the ability
to let guests choose music which in turn incorporates everyone's taste.
Furthermore, the party host does not have to worry about catering to the guests' varied music tastes.

\section{Context}
The problem revolves around social gatherings of any kind that involve music.
Parties, Weddings, and Conferences are prime examples. Nobody wants to be at an
event where the guests aren't feeling the music. The dance floor will be
empty, and the mood will be somber. This is the type of situation our app
remedies. Music that everybody enjoys will lift the guests moods, and make
the event more fun.

\section{Stakeholders}
People who attend events and those who organize them are stakeholders of
our product. It is important to make sure that people hear what they want,
rather than being forced to listen to what someone else decides.

\section{Environment}
\textcolor{blue} {
The product should work on a wide variety of platform and environments. The personal mobile device or computer that a user owns should not be a hamper on their ability to use the product.
}

\end{document}
